---
title: "Eating Out"
author: "Rachel Polack"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```



```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```
based on frequency table above, which shows the volume of people who eat out and people who do not eat out for each racial group, we can see that about 950 white people eat out while about 200 do not. Meanwhile, about 200 black people eat out while about 100 people do not. For the other racial groups, about 100 people eat out while about 50 do not. Putting this into percentages , 80% of white people eat out while 20% do not. meanwhile black and others have about the same percentages with 70% of people eat out while 30% do not.

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
The numerical summery above shows that the actual values of the percentages of people who eat out and do not eat out for each racial groups. the data above confirms the estimations from the graphical results, and it shows that for white people, 83.13% eat out and 16.87% do not. Similar to the observations made previously, black people and others have a similar ratio of about 70% of people who eat out while 30% of people who do not. Furthermore, the table above shows that white people will make up tha majority of the people who claim that they eat out. Specifically, among the people answered yes to eating out, 81.69% were white while 11.83% were black, and 6.48% were others.

